Representing Scenes as Light Fields for Real Time Rendering in Virtual Reality Display

### 2021-01-19 TOG/1-introduction.tex
snapshot

\note{
What prior works have done, and why they are not adequate.
(Note: this is just high level big ideas. Details should go to a previous work section.)
}%note
\qisun{(Jan 5, 2021) We should include two main fields: neural representation and foveated rendering}

@@

We validate our approach by conducting both numerical analysis and user evaluations on commercially available AR/VR display devices. They both reveal the effectiveness of our method on delivering a real-time VR viewing experience, perceptually identical to an arbitrarily high quality rendered 3D scene, without compromising on local storage volume. Our main contributions include the following:
\begin{itemize}
    \item A low-latency and significantly low-storage 6DoF immersive application that preserves perceptual quality
    \item A gaze-contingent neural representation and synthesis method tailored for first-person viewing
    \item A spatio-temporally joint optimization for balancing latency and perceptual quality
\end{itemize}

>>>>

\note{
What prior works have done, and why they are not adequate.
(Note: this is just high level big ideas. Details should go to a previous work section.)
}%notez
\qisun{(Jan 5, 2021) We should include two main fields: neural representation and foveated rendering}

@@

We validate our approach by conducting both numerical analysis and user evaluations on commercially available AR/VR display devices. They both reveal the effectiveness of our method on delivering a real-time VR viewing experience, perceptually identical to an arbitrarily high quality rendered 3D scene, without compromising on local storage volume. Our main contributions include the following:
\begin{itemize}
    \item A low-latency and significantly low-storage 6DoF immersive application that preserves perceptual quality
    \item A gaze-contingent scene parameterization and neural representation/synthesis method tailored for first-person viewing
    \item A spatio-temporally joint optimization for balancing latency and perceptual quality
\end{itemize}

### 2021-01-19 TOG/2-prior.tex
snapshot

\subsection{Deep View Synthesis}

\subsection{Gaze-Contingent Rendering}
\cite{Guenter:2012:F3G,Patney:2016:TFR,Sun:2017:PGF,Kaplanyan:2019:DNR}

>>>>

\subsection{Image-based View Synthesis}
Image-based rendering (IBR) has been proposed in computer graphics to complement the traditional 3D mesh + ray propagation pipelines \cite{levoy1996light,gortler1996lumigraph}. Benefiting from the 2D representation, it delivers pixel-wise fast rendering quality without compromising performance. However, one major limitation of IBR is the demand of large volume pre-captured data. This requires significant large volume of data and limited view ranges. 
To address this problem, recent years have witnessed extensive research on synthesizing novel views instead of storing. Examples include synthesizing light fields \cite{LearningViewSynthesis}, panoramas \cite{Lin:DeepPanorama}, and volumetric videos \cite{Broxton:immersiveLF}. However, despite being more compact, the synthesis is usually in a locally interpolated fashion than being globally consistent.

\subsection{Implicit Scene Representation for Neural Rendering}
To fully represent a 3D object and environment without storing images and meshes, neural representations have drawn attentions in both computer graphics and computer vision communities. With a implicit deep neural network and 3D world tailored format, it generates an objects appearance given a camera pose \cite{sitzmann2019deepvoxels,sitzmann2019srns,sitzmann2019siren,mildenhall2020nerf}. 
However, current implicit representations focuses on ``out-side-in'' view with single objects. In immersive medias, the cameras are typically user-centered, resulting in lack of coverage thus quality drop. Instead of full scene representation, our method is VR tailored via representing the scene for user-centered views.

\subsection{Gaze-Contingent Virtual Reality Rendering}
Both rendering and neural synthesis suffers from computational load, thus computational and transmissional latency.
With a full mesh representation, foveated rendering has been proposed to proposed to accelerate local rendering performance \cite{Guenter:2012:F3G,Patney:2016:TFR,Sun:2017:PGF,Kaplanyan:2019:DNR}. This is typically achieved through high-field-of view displays (such as VR HMDs) and eye-trackers. 
In comparison, synthesizing views if far from being real-time or interactive. Our method introduces the vision-matched deep synthesis with both high quality and low latency, suitable for cloud-based and local representations.
